\documentclass{book}
\usepackage[margin=1in]{geometry}

\title{Pubs and People - Alpha}
\author{Sorcerers of the seaside ltd.}

\begin{document}
\maketitle

\section{Introduction}
The Pubs and People RPG is is about storying telling in worlds of people and pubs. It share elements with adult games and night-out-on-the-town-with-the-boyz. Simmilar to those games this is driven by imagination - It's about picturing the twoering stein glass beneith an oddly we paper coaster (odd you donn't seem to ever remember using it, so how could it be wet?)

In the People and Pubs game, you create a person. It has been theorised by many people that we live inside another game very simmilar to Pubs and People, called Dungeons and Dragons; the same people has extrapolated this theory out to say that subconciously the characters we play in People \& Pubs are the the people controlling us in Dungeons and Dragons. Here at Sorcerers of the Seaside we adimantly refuse this assertion, stating that this is a rumour created by a previous member Oregano because he left the party before he ever got the chance to take part in the million-gold-peice enterprise that is Sorcers of the Seasonside ltd. Your person is meant to team up with other people in the pub, inside the pubs and people peoples pub, and work together to play the people inside the pub inside the pubs and people RPG.
\newline
\newline
\emph{WARNING: Character inside People-and-Pubs have been known to become sentient and create their own RPG is left unattended for long periods of time, this is highly dicouraged.}
\newline
\newline
There is another character inside the pubs and peoples peoples pubs, and this is the landlord of the people inside the pubs and peopless pub. The pub-landlord is diesigned to design the night out. The lordland might might desicribe their entrance into the Golden Lion pub, inside a vilianous den called Romford, amoung other scenarios. Because the LL can improvise or react to anything the peoples pubs peoples, people and pubs is infinaltey flexible, and each night out can be exciting and unexpected.

The game has no real end - When one night out ends, another one can begin, you can possiblky even carry the adventure on into the day, however this is likley end up up with your characters devloping an alchohol addiction. This will gradually eat away at their sanity stat over a lord period of time. This is a child friendly game and we do not wan't to encourage this behaviour. You cannot win this game, when alhohol is involved you only loose, and for this reason with every copy of the People-and-Pubs payers handbook we include a couon for a local 10-step program.

\section{Creating a person}
Your first step in your People-and-Pubs aventure is to make the person who will drink in the pub. A character is a combination of game stats, roleplaying hooks =1~~, and subliminal messages from the person controlling you~~. You may be tempted to put thought into what kind of character you wantto be, or hes/her backstory - Dont.

Every P\&P character is a specific type of persona all of which are detailed below

\subsection{Chav}
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Improvised wepon:} In the event of a pub brawl a chav can use hes resourceful nature to find an improvised wepon i.e. broken bottle
    \item \textbf{Broken Language:} Chavs by default are born with accsess to speak broken-common-tounge; a dialect of common tounge with long and complex terms removed, which other personas 
    \item \textbf{JSA:} Chavs while without a job inside P\&P by default collect an amount of money (deicded by the landlord) once a week, however if they get a job they cannot collect this
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Low inteligence:} Chavs by default have low inteligence, however they can have average or above average wisdom
    \item \textbf{Fake Gucci flip flop:} Chavs often wear counterfeit armour which can give them an edge in intimidation rolls, however in battle these garments offer no real benefit. A percetption roll can be done to detect is the garment is counterfeit or not
    \item \textbf{Shit music taste:} If a chav encounters a musical artist, if the artist makes a performance roll the trational 1-20 meaning is reversed. A nat 1 is equivilent to a nat 20 for a chav, and vise-versa
\end{itemize}
\subsubsection{Appearance}
\begin{itemize}
    \item \textbf{Fake Tan:} Female chavs are have an organge glow about them, simulating health. This is typicall synthetic however, and during application he/she will have to roll for how good a job it is. The outcome of this roll will dictate the perception roll for other people to notice
    \item \textbf{Fake gucci flip flop:} See fake gucci flip flop entry in chav traits
    \item \textbf{Unpleasent smell:} Chavs typically paratke in the use of a substance called "amber leaf", which causes them to have an unpleasent smell about the. When other people are in close proximity to a chav they must roll a constitution save to overcome this.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
    \item \textbf{Obnoxious:} Chavs give little care of the effect their nature has on those around them, weather this is out of spite or gneral social unawareness is up for debate
    \item \textbf{Poor financial skills:}  Chavs will usually have no money, and in the event they get a large amount they will experiance the need to spend it
    \item \textbf{Lack of understanding of basic concepts:} This goes hand in hand with lack of inteligence
    \item 
\end{itemize}

\subsection{Goth}
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Gloom:} The character can create a sense of melancholy and sadness in the pub, lowering the morale of other patrons.
    \item \textbf{Gothic Fashion Sense:} Provides a bonus to any charisma-based checks when interacting with other patrons who are also gothic or have similar fashion sense. 
    \item \textbf{Dark poetry recitation:} Can be used to impress or intimidate other patrons.
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Darkvision:} Can see in the dark as if it were dim light.
    \item \textbf{Gloom aura:} Radiates an aura of melancholy, making it harder for others to feel happy in their presence.
    \item \textbf{Gothic resistance:} Has advantage on saving throws against spells and effects that would cause them to feel cheerful or happy.
\end{itemize}

\subsubsection{Appearance}
\begin{itemize}
    \item Pale skin, often with dark hair styled in an alternative fashion.
    \item May have unusual eye color, such as red or purple.
    \item Wears dark, gothic clothing, with tattoos or piercings.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
    \item Introverted, preferring to keep to themselves in the corner of the pub.
    \item Strong sense of individuality and a desire to stand out from the crowd. 
    \item Pessimistic or nihilistic outlook on life.
\end{itemize}
\subsubsection{Equipment}
\begin{itemize}
    \item Small notebook for writing dark poetry.
    \item Leather jacket.
    \item Pair of combat boots.
\end{itemize}
\subsubsection{Culture}
\begin{itemize}
    \item Values individuality and self-expression.
    \item Has a fondness for dark or "edgy" music, poetry, and art.
    \item May be perceived as gloomy or strange by other races, but fiercely loyal to their own kind.
\end{itemize}

\subsection{Retired old man}
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Wisdom of the Ages:} Can provide advice and knowledge based on their many years of experience.
    \item \textbf{Recall of Stories:} Can regale other patrons with tales from their life, providing entertainment and potentially impressing them. 
    \item \textbf{"I've seen it all" demeanor:} Provides a bonus to any Wisdom (Insight) checks to determine if someone is being truthful or sincere.
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Decreased mobility:} Has disadvantage on any physical checks that require speed or agility.
    \item \textbf{Keen senses:} Has advantage on Wisdom (Perception) checks to notice details in their surroundings.
    \item \textbf{Calm demeanor:} Has advantage on saving throws against being frightened.
\end{itemize}
\subsubsection{Appearance}
\begin{itemize}
    \item Wrinkled skin, grey or white hair.
    \item Often seen wearing slippers and a comfortable cardigan.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
    \item Enjoys taking things slow and easy.
    \item Has a wealth of life experience and often dispenses advice to those who will listen.
    \item Loves to tell stories from their life, and can often be found in the pub regaling other patrons with tales.
\end{itemize}
\subsubsection{Equipment}
\begin{itemize}
    \item A cane for support when moving around.
    \item A pocket watch that has been passed down for generations.
    \item A small photo album filled with pictures from their life.
\end{itemize}
\subsubsection{Culture}
\begin{itemize}
    \item Values the simple pleasures in life, such as good company and a cold drink.
    \item Has a great appreciation for the wisdom and experiences of their years.
    \item Often seen as a mentor figure by other patrons of the pub.
\end{itemize}

\subsection{Working man}
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Strength of the Laborer:} Provides a bonus to any physical checks, such as lifting heavy objects or breaking down doors.
    \item \textbf{Work Ethic:} Can work tirelessly for extended periods of time without getting tired, providing a bonus to any Constitution checks. 
    \item \textbf{Intimidating Stare:} Can be used to intimidate other patrons, providing a bonus to any Charisma (Intimidation) checks.
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Tough and Calloused:} Has resistance to damage from non-magical weapons.
    \item \textbf{Manual Dexterity:} Has advantage on any checks that require fine motor skills, such as repairing equipment or picking locks.
    \item \textbf{Grit and Determination:} Has advantage on saving throws against being charmed or intimidated.
\end{itemize}
\subsubsection{Appearance}
\begin{itemize}
    \item Muscular build, often with rough hands and forearms.
    \item Wears practical work clothes, such as denim overalls, a hard hat, and work boots.
    \item May have a beard or mustache.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
    \item Hardworking and reliable, with a sense of duty to their job and their family.
    \item Down-to-earth and straightforward, with little patience for fancy talk or pretentiousness.
    \item Can be hot-tempered and stubborn at times.
\end{itemize}
\subsubsection{Equipment}
\begin{itemize}
    \item Work gloves and safety goggles.
    \item Tool belt with a hammer, screwdriver, and wrench.
    \item Thermos of coffee or other preferred beverage.
\end{itemize}
\subsubsection{Culture}
\begin{itemize}
    \item Values hard work and self-sufficiency.
    \item Often has a blue-collar job, such as a construction worker, factory worker, or mechanic.
    \item May have a strong sense of community and loyalty to their fellow workers or their neighborhood.
\end{itemize}

\subsection{Drunk College Girl}
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Liquid Courage:} Gains a bonus to charisma-based checks when interacting with other patrons while under the influence of alcohol.
    \item \textbf{Wild Dancing:} Can use their impressive dance skills to impress or entertain other patrons.
    \item \textbf{Social Butterfly:} Has a natural talent for making friends and networking in social situations.
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Alcohol Tolerance:} Has advantage on saving throws against the negative effects of alcohol.
    \item \textbf{Impulsive:} Tends to act on their emotions and desires without considering the consequences.
    \item \textbf{Risk-taker:} Will often take dangerous or reckless actions for the sake of fun or excitement.
\end{itemize}

\subsubsection{Appearance}
\begin{itemize}
    \item Bold, attention-grabbing clothing.
    \item May have colorful or wild hairstyles.
    \item Often seen with a drink in hand.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
    \item Outgoing and extroverted.
    \item Enjoys the party lifestyle and is always up for a good time.
    \item Can be impulsive and unpredictable.
\end{itemize}
\subsubsection{Equipment}
\begin{itemize}
    \item A flask or other alcohol container.
    \item A pair of comfortable shoes for dancing.
    \item A phone with a large social media following.
\end{itemize}
\subsubsection{Culture}
\begin{itemize}
    \item Values having a good time and making new connections.
    \item Enjoys attending parties and events, and may be seen as the life of the party.
    \item May be perceived as superficial or shallow by other races, but can be fiercely loyal to their friends.
\end{itemize}

\subsection{Furry}
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Animalistic Charm:} The character can use their furry appearance to charm other patrons into doing what they want.
    \item \textbf{Furry Knowledge:} Provides a bonus to any intelligence-based checks when interacting with other patrons who are also furries or have knowledge of the furry fandom.
    \item \textbf{Furry Roar:} Can be used to impress or intimidate other patrons.
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Keen Senses:} Has advantage on Wisdom (Perception) checks to notice details in their surroundings, particularly related to animal behavior.
    \item \textbf{Furry Aura:} Radiates an aura of playful energy, making it harder for others to resist joining in their antics.
    \item \textbf{Furry Resistance:} Has advantage on saving throws against spells and effects that would cause them to lose interest in or be averse to animal-related activities.
\end{itemize}
\subsubsection{Appearance}
\begin{itemize}
    \item Covered in fur, resembling an anthropomorphic animal.
    \item May have animal ears, a tail, or both.
    \item Often wears animal-themed clothing or accessories.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
\item Outgoing and playful, often encouraging others to join in on their fun.
\item Strong sense of belonging within the furry community and a desire to express themselves through their fursona.
\item May be perceived as strange or eccentric by other races, but fiercely loyal to their own kind.
\end{itemize}
\subsubsection{Equipment}
\begin{itemize}
    \item A fursuit or partial fursuit for public events.
    \item Various animal-themed accessories, such as paw gloves or a tail.
\end{itemize}
\subsubsection{Culture}
\begin{itemize}
    \item Values creativity and self-expression, particularly through artwork and performance.
    \item Has a love of animals and a desire to embody their traits.
    \item Often seen at conventions and meetups for furries.
\end{itemize}

\subsection{Polish man}
\linebreak
\linebreak
\emph{Please note: A controversy has be raise over the use of gendered terms inside the race names in People and Pubs potential Peoples personas inside the P&P pubs. We would like to make it clear that it is very possible to be a female Polish man.}
\linebreak
\linebreak
\subsubsection{Abilities}
\begin{itemize}
    \item \textbf{Tough as Nails:} Provides a bonus to any Constitution checks to withstand physical harm.
    \item \textbf{Street Smarts:} Has a good understanding of how to navigate social situations and can provide a bonus to any Charisma checks.
    \item \textbf{Devastating Haymaker:} Can unleash a powerful punch, providing a bonus to any physical attack rolls.
\end{itemize}
\subsubsection{Traits}
\begin{itemize}
    \item \textbf{Resilient:} Has resistance to cold and can withstand harsh weather conditions.
    \item \textbf{Multilingual:} Has the ability to speak multiple languages, providing a bonus to any Intelligence checks to decipher languages or communicate with others.
    \item \textbf{Battle-Tested:} Has advantage on saving throws against fear.
\end{itemize}
\subsubsection{Appearance}
\begin{itemize}
    \item Muscular build, with a rough and weathered appearance.
    \item Often wears work clothes or plain, practical clothing.
    \item May have scars or other signs of physical damage.
\end{itemize}
\subsubsection{Personality}
\begin{itemize}
    \item Friendly and welcoming, with a strong sense of camaraderie towards other immigrants and hardworking individuals.
    \item Can be stern and direct when necessary, but generally prefers to resolve conflicts through diplomacy.
    \item Respects strength and is willing to stand up for himself and others if provoked.
\end{itemize}
\subsubsection{Equipment}
\begin{itemize}
    \item Heavy boots and durable work gloves.
    \item A small knife for protection.
    \item A worn, but reliable, wristwatch.
\end{itemize}
\subsubsection{Culture}
\begin{itemize}
    \item Comes from a former Soviet bloc country and has a strong sense of national pride and history.
    \item Works a manual labor job and often goes to the pub after work to unwind.
    \item May have a community of fellow immigrants from their home country that they associate with.
\end{itemize}

\end{document}